\Large Feature and order manipulations in a free recall task affect memory for current and future lists

### 2023-11-21 paper/main.tex
recompiled changes doc

%! suppress = LineBreak
\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage[font=small,labelfont=bf]{caption}
\usepackage{geometry}
\usepackage[sort&compress]{natbib}
\usepackage{pxfonts}
\usepackage{graphicx}
\usepackage{setspace}
\usepackage{hyperref}
\usepackage{lineno}
\usepackage{amsopn}
\usepackage{rotating}
\usepackage{booktabs}
\usepackage[table]{xcolor}

@@

\caption{\textbf{Comparing accuracy on late lists in order-manipulatation
versus feature-rich conditions.} The $t$-tests reported in the table were
carried out across-participants, and reflect data aggregated across all late
lists from each participant. Abbreviations used in this table are defined in
Table~\abbreviations.}

@@

\caption{\textbf{Comparing temporal clustering on late lists in order-manipulatation
versus feature-rich conditions.} The $t$-tests reported in the table were
carried out across-participants, and reflect data aggregated across all late
lists from each participant. Abbreviations used in this table are defined in
Table~\abbreviations.}

@@

\caption{\textbf{Comparing feature-based clustering on late lists in semantic order-manipulatation
versus feature-rich conditions.} The $t$-tests reported in the table were
carried out across-participants, and reflect data aggregated across all late
lists from each participant. Abbreviations used in this table are defined in
Table~\abbreviations.}

@@

\caption{\textbf{Comparing feature-based clustering on late lists in
lexicographic order-manipulatation versus feature-rich conditions.} The
$t$-tests reported in the table were carried out across-participants, and
reflect data aggregated across all late lists from each participant.
Abbreviations used in this table are defined in Table~\abbreviations.}

@@

\caption{\textbf{Comparing feature-based clustering on late lists in visual order-manipulatation
versus feature-rich conditions.} The $t$-tests reported in the table were
carried out across-participants, and reflect data aggregated across all late
lists from each participant. Abbreviations used in this table are defined in
Table~\abbreviations.}

>>>>

\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage[font=small,labelfont=bf]{caption}
\usepackage{geometry}
\usepackage[sort&compress]{natbib}
\usepackage{pxfonts}
\usepackage{graphicx}
\usepackage{setspace}
\usepackage{hyperref}
\usepackage{lineno}
\usepackage{amsopn}
\usepackage{rotating}
\usepackage{booktabs}
\usepackage[table]{xcolor}

@@

\caption{\textbf{Comparing accuracy on late lists in order-manipulation
versus feature-rich conditions.} The $t$-tests reported in the table were
carried out across-participants, and reflect data aggregated across all late
lists from each participant. Abbreviations used in this table are defined in
Table~\abbreviations.}

@@

\caption{\textbf{Comparing temporal clustering on late lists in order-manipulation
versus feature-rich conditions.} The $t$-tests reported in the table were
carried out across-participants, and reflect data aggregated across all late
lists from each participant. Abbreviations used in this table are defined in
Table~\abbreviations.}

@@

\caption{\textbf{Comparing feature-based clustering on late lists in semantic order-manipulation
versus feature-rich conditions.} The $t$-tests reported in the table were
carried out across-participants, and reflect data aggregated across all late
lists from each participant. Abbreviations used in this table are defined in
Table~\abbreviations.}

@@

\caption{\textbf{Comparing feature-based clustering on late lists in
lexicographic order-manipulation versus feature-rich conditions.} The
$t$-tests reported in the table were carried out across-participants, and
reflect data aggregated across all late lists from each participant.
Abbreviations used in this table are defined in Table~\abbreviations.}

@@

\caption{\textbf{Comparing feature-based clustering on late lists in visual order-manipulation
versus feature-rich conditions.} The $t$-tests reported in the table were
carried out across-participants, and reflect data aggregated across all late
lists from each participant. Abbreviations used in this table are defined in
Table~\abbreviations.}
